MSD panels 1, 2 and 3 HVE Supernatant

### 2016-09-21 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
update?

---
title: "MSD panels 1, 2 and 3 HVE Supernatant"
output: pdf_document
---

@@

ggplot(avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet, aes(x = Timepoint, y = avgEstConc))+
   geom_point(aes(color = Donor), alpha = 0.75, size = 3)+
  scale_y_log10()+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations by Donor, Timepoint and Condition")

################## another way of making the plots #########

#make a list of the analytes

#I'm using a unique vector here instead of the levels of Assay because I don't want to include IFNa2a OR Il-7. There weren't any data points in the detection range for those analytes (so I don't want to try to make a plot of it)

# analyteList<-as.list(unique(avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet$Assay))

# #write a function to make a plot for each analyte
# 
# plotAnalytes <- function (Analyte){
#    avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet %>%
#      filter(Assay == Analyte)%>%
#      
#      ggplot( aes(x = Timepoint, y = avgEstConc))+
#    geom_point(aes(color = Donor ), alpha = 0.5, size = 3)+
#   geom_line(aes(group = Donor, color = Donor), alpha = 0.5)+
#     stat_summary(fun.y = mean, geom = "point")+
#     stat_summary(fun.y = mean, geom = "line",aes(group = 1))+
#    scale_shape_manual(values = c("Above Fit Curve Range" = 1, "Below Detection Range" = 1, "In Detection Range" = 16))+
#    scale_y_log10()+
#    labs( y = "Concentration pg/ml")+
#   facet_wrap(~Virus, scales = "free_x")+
#    theme(axis.text.x = element_text(size = 11))+
#      ggtitle(Analyte)
# }
# 
# 
# 
# lapply(analyteList, FUN = plotAnalytes)

>>>>

---
title: "MSD panels 1, 2 and 3 HVE Supernatant"
output: html_document
---

@@

ggplot(mergeMock, aes(x = Timepoint, y = MockSubtracted))+
   geom_point(aes(color = Donor), alpha = 0.75, size = 3)+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations by Donor, Timepoint and Condition")
